DisCon Children 6 exposure trials

### 2019-03-21 analysis/02_kids_600.Rmd
update kids analysis

---
title: "DisCon Kids Pilot"
output: html_document
  code_folding: hide
---

@@

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

>>>>

---
title: "DisCon Children 6 exposure trials"
output: html_document
  code_folding: hide
---

@@

kbm1 <- brm(correct_target1 ~ age_num +
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)
